\documentclass[12pt]{article}%
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage{wasysym}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{stackengine}
\def\stackalignment{l}
\usepackage[colorlinks]{hyperref}
\usepackage{tikz}
\usepackage[export]{adjustbox}

%\usepackage{geometry}
%\geometry{top = 0.9in}
\usepackage{appendix}

\newcounter{subfigure}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\N}{\mathbb{N}}
\renewcommand{\S}{\mathbb{S}^1}
\renewcommand{\Re}{\text{Re}}
\newcommand{\ea}{\textit{et al. }}
\renewcommand{\epsilon}{\varepsilon}
\renewcommand{\th}{\text{th}}
\newcommand{\sgn}{\operatorname{sgn}}

\renewcommand{\setminus}{\smallsetminus}

\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}

\definecolor{red}{rgb}{0.8500, 0.3250, 0.0980}
\definecolor{green}{rgb}{0.4660, 0.6740, 0.1880}
\definecolor{yellow}{rgb}{0.9290, 0.6940, 0.1250}
\definecolor{blue}{rgb}{0, 0.4470, 0.7410}


\begin{document}

\title{Coding Project 2:  Parsing musical frequency signatures}

\author{Your Name}
\date{}

\maketitle


\begin{abstract}
{\color{red} [[Short abstract (5 or 6 sentences) stating in plain language what you did in the project.]]}
\end{abstract}


\section{Introduction}
\label{Sec: Intro}

{\color{red} [[1 short paragraph on musical notes and their associated frequencies, and anything else you may want to add about this particular clip.  No need to reference anything, just want you to get into the habit of thinking about science from a historical/societal aspect.  Also, feel free to get this from the book and wikipedia, just paraphrase to avoid plagiarism.]]}

\bigskip
\bigskip

{\color{red} [[1 paragraph outlining the remainder of the report.]]}


\section{Theoretical Background}

{\color{red}[[A sentence or two on what you'll talk about in this section.]]}


\subsection{The Gabor Transform}

{\color{red}[[1 or 2 paragraphs going over the derivation of the Gabor Transform and add some exposition explaining the derivation.  This can be taken directly from the book/lecture, but paraphrase to avoid plagiarism.]]}


\subsection{The Discrete Gabor Transform}

{\color{red}[[1 or 2 paragraphs going over the derivation of the Discrete Gabor Transform and add some exposition explaining the derivation.  This can be taken directly from the book/lecture, but paraphrase to avoid plagiarism.]]}


\section{Numerical Methods}

{\color{red}[[Explain in detail what the code does (about 3 or so paragraphs based on the number of distinct steps that are necessary).   Feel free to break this up in sections or keep it all in one section.]]}


\section{Results}

{\color{red}[[Put your result plots here.  Explain the plots (a paragraph for each).  Make sure the caption for your figure can be understood without having to read the exposition.]]}


\section{Conclusion}\label{Sec: Conclusion}

{\color{red}[[A paragraph summarizing the report.]]}


{\color{red}[[1 paragraph:  What are some things you learned from the project.  What are some drawbacks of this technique.  {\color{blue} Can you recognize the song?  It's ok if you don't recognize it :).}]]}


\section*{Acknowledgment}

{\color{red}[[You are welcome to get help on the project from others:  students in the class, TAs, stack overflow, etc.  Just make sure to thank anyone who helped you on the project.  If you truly didn't get any help from anyone, please feel free to skip this section.]]}


\bigskip
\bigskip
\bigskip

{\color{red}[[Don't worry about references.]]}


\end{document}
